---
title: "Gapminder Exploration"
output: rmarkdown::github_document
---
##Get the Gapminder data
Work with some of the data from the [Gapminder project](http://www.gapminder.org). Since the package is already installed, we just need to load it, also load the package that are useful for analyzing the data.

```{r}
library(gapminder)
library(tidyverse)
library(ggplot2)
```


Have a look at the data:
```{r}
glimpse(gapminder)
dim(gapminder)
```

Explore the variable *"pop"*
```{r, fig.width=12, fig.height=6}
min(gapminder$pop)
max(gapminder$pop)
ggplot(gapminder, aes(y = pop)) + geom_boxplot(aes(x = factor(1))) +  facet_wrap(~continent, scales = "free")
```

Because gapminder has too much info, in my work, I just extract the data that belong to the continent of Asia, and variables *"country"*, *"year"*, and *"pop"*.
```{r}
gDat <- gapminder[gapminder$continent == "Asia", c("country", "year", "pop")]
str(gDat)
```

Plot annual population for different countries in Asia 
```{r, fig.width=12, fig.height=5}
ggplot(gDat, aes(x = year, y = pop)) + geom_point(aes(color = country)) 
```

